The Impact on Job Interest of Beginner Programmers

### 2021-04-08 outputs/paper/paper.Rmd
Add regression model

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
library(PerformanceAnalytics)
```

@@

# Data
```{r}
#### Message ####
# Show code for reviewers
#
# // Variables
# Y: MoneyForLearning
# X: Age, CityPopulation, CommuteTime, Income, MonthsProgramming, SchoolDegree
# c: Gender
# 
# // Clean csv
# https://github.com/bonjwow/new-coders/blob/main/inputs/data/clean_new-coders.csv
#
#

@@

```{r}
#### Test internal consistency with Cronbach's alpha ####
psych::alpha(dfNewCoders)
```

@@

# Model

>>>>

library(tidyverse)
library(dplyr)
library(stargazer)
library(psych)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
```

@@

# Data
```{r, include=FALSE}
#### TODO's ####
# Explain raw data 
#
```

```{r}
#### Message ####
# Show code for reviewers
#
# // Variables
# Y: MoneyForLearning
# X: Age, CityPopulation, CommuteTime, Income, MonthsProgramming, SchoolDegree
# c: Gender
# 
# // Clean csv
# https://github.com/bonjwow/new-coders/blob/main/inputs/data/clean_new-coders.csv
#
#

@@

@@

# Model
```{r, include=FALSE}
#### TODO's ####
# Write out what each variable is
# Weaknesses and next steps
```

```{r}
#### Multiple regression analysis ####
summary(fit.lm <- lm(formula = 
                       MoneyForLearning ~ 
                       Gender +
                       CityPopulation +
                       CommuteTime +
                       Income +
                       MonthsProgramming +
                       SchoolDegree, 
                     data = dfNewCoders))
```
```{r}
#### Beta ####
QuantPsyc::lm.beta(fit.lm)
```

```{r}
#### Check multicollinearity with Variance Inflation Factor (VIF) & Tolerance ####

### VIF
car::vif(fit.lm)
### Tolerance
1/car::vif(fit.lm)
```

```{r}
